---
title: "**Genepar: Pain Intensity & Medication Use**"
author: "Vivek Verma"
date: "`r lubridate::today()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("haven")
library("tidyverse")
library("plotly")
library("kableExtra")
library("jtools")
library("lme4")
library("effects")
library("data.table")
options(knitr.kable.NA = '')
theme_set(
  theme_classic() +
    theme(legend.position = "top")
  )
```

## **Data Summary**

```{r include=T, warning=F,message=F}
df <- readRDS("./genepar/GENEPAR1.RDS")
summary(df[,-1]) %>%
  kbl(caption = "Summary of all variables") %>%
  kable_classic("hover", html_font = "Cambria", full_width = F) %>% scroll_box(width = "100%")
```

### Pain (NRS)

#### Pain scores were collected at the baseline and follow-up visits

#### using the following question:

#### \*\* *In the past 7 days, how would you rate your lower back pain on average? (0-10 scale)* \*\*

```{r fig.align='center', message=FALSE, warning=FALSE, include=T}
dfl <- readRDS("./GENEPAR1_long.RDS")
df.summary <- dfl %>%
  group_by(DIAGNOSIS,TIME,SEX) %>%
  dplyr::summarise(
    Pain = mean(PAIN_NRS, na.rm = T),
    n = n(),
    sd = sd(PAIN_NRS, na.rm = T),
    se = sd/sqrt(n))
df.summary  %>%
  kbl(caption = "Summary of Pain") %>%
  kable_classic("hover", html_font = "Cambria", full_width = T)
# plot
pd <- position_dodge(0.2)
  ggplot(df.summary, aes(x=TIME, y=Pain, colour=SEX, group=SEX)) + 
    geom_errorbar(aes(ymin=Pain-sd, ymax=Pain+sd, colour=SEX),
                  width=0.2, position=pd, lwd = 2) +
    geom_line(aes(colour=SEX),position=pd, lwd = 2) +
    geom_point(aes(fill=SEX),position=pd, size=4, shape=21) +
  scale_fill_manual(values = c("#F062F1","#3A27D4"))  +
  scale_color_manual(values = c("#F062F1","#3A27D4")) +
    labs(title = "Change in pain scores",
         x = "Time",
         y = "Pain (NRS)",
         caption = "Errorbars represent SD") +
    ylim(-0.2,10.2) +
    facet_wrap(~DIAGNOSIS)

```

### Distribution of the change in pain

```{r fig.align='center', message=FALSE, warning=FALSE, include=T}
df$PAIN_CHANGE <- df$PAIN_FOLLOW_UP - df$PAIN_BASELINE
ggplotly(ggplot(df, aes(x = PAIN_CHANGE)) + 
             geom_histogram(aes_string(fill = "..count..",
                                       color = "..count.."),
                            binwidth = 1) +
             scale_fill_gradient(low="gray",high="red") +
             scale_color_gradient(low="gray",high="red") +
             xlab("Change in pain score") + theme_bw() +
             theme(legend.position = "none")+facet_wrap(~SEX))
```

### **Pain Medication data**

#### Note that the drug classes: **NSAIDS** and **OPIOIDS** were implicitly enriched. E.g.: ACETAMINOPHEN AND CODEINE is counted as **OPIOIDS** (not as ACETAMINOPHEN)

#### Also, **NSAIDS** were preferably enriched over OPIOIDS. E.g.: IBUPROFEN AND CODEINE is counted as **NSAIDS** (not as OPIOIDS)

### Pain medications at **baseline (M00)**:

```{r include=T, warning=F,message=F}
df1 <- read_sas("/mnt/nfs/backup/data/quebec_pain_registry/outdir/in00_pmed_actuell_boni.sas7bdat",
                "/mnt/nfs/backup/data/quebec_pain_registry/outdir/formats.sas7bcat")
df1 <- df1 %>% dplyr::select(c(ID,NQ00_CPM_ACT))
df1 <- unique(df1)
df1$MED <- NA
df1$MED[grep("ACETAMINOPH",df1$NQ00_CPM_ACT)] <- "ACETAMINOPHEN"
df1$MED[grep("GABA",df1$NQ00_CPM_ACT)] <- "GABA_ANALOGS"
df1$MED[grep(pattern = "MORPH|CODONE|CODEINE|CODÉINE|METHADONE|TRAMADOL|FENTANYL|TAPENTADOL",
             df1$NQ00_CPM_ACT)] <- "OPIOIDS"
df1$MED[grep(pattern = "PROFEN|NAPROX|KETORO|COXIB|FENAC",
             df1$NQ00_CPM_ACT)] <- "NSAIDS"
df1$MED[is.na(df1$MED)] <- "OTHER"
table(df1$NQ00_CPM_ACT,df1$MED) %>%
  kbl(caption = "Baseline pain medication classification") %>%
  kable_classic("hover", full_width = T, html_font = "Cambria") %>% 
  scroll_box(width = "100%", height = "500px")
df1 <- df1[,c(1,3)]
df1 <- unique(df1)
df1$TIME <- "M00"
```

### Pain medications at **follow-up (M06 and M12)**:

```{r include=T, warning=F,message=F}
df2 <- read_sas("/mnt/nfs/backup/data/quebec_pain_registry/outdir/in06_pmed_actuell_boni.sas7bdat",
                "/mnt/nfs/backup/data/quebec_pain_registry/outdir/formats.sas7bcat")
df2 <- df2 %>% dplyr::select(c(ID,NQ06_CPM_ACT))
df2 <- unique(df2)
df2$MED <- NA
df2$MED[grep("ACETAMINOPH",df2$NQ06_CPM_ACT)] <- "ACETAMINOPHEN"
df2$MED[grep("GABA",df2$NQ06_CPM_ACT)] <- "GABA_ANALOGS"
df2$MED[grep(pattern = "MORPH|CODONE|CODEINE|CODÉINE|METHADONE|TRAMADOL|FENTANYL|TAPENTADOL",
             df2$NQ06_CPM_ACT)] <- "OPIOIDS"
df2$MED[grep(pattern = "PROFEN|NAPROX|KETORO|COXIB|FENAC",
             df2$NQ06_CPM_ACT)] <- "NSAIDS"
df2$MED[is.na(df2$MED)] <- "OTHER"

df3 <- read_sas("/mnt/nfs/backup/data/quebec_pain_registry/outdir/in12_pmed_actuell_boni.sas7bdat",
                "/mnt/nfs/backup/data/quebec_pain_registry/outdir/formats.sas7bcat")
df3 <- df3 %>% dplyr::select(c(ID,NQ12_CPM_ACT))
df3 <- unique(df3)
df3$MED <- NA
df3$MED[grep("ACETAMINOPH",df3$NQ12_CPM_ACT)] <- "ACETAMINOPHEN"
df3$MED[grep("GABA",df3$NQ12_CPM_ACT)] <- "GABA_ANALOGS"
df3$MED[grep(pattern = "MORPH|CODONE|CODEINE|CODÉINE|METHADONE|TRAMADOL|FENTANYL|TAPENTADOL",
             df3$NQ12_CPM_ACT)] <- "OPIOIDS"
df3$MED[grep(pattern = "PROFEN|NAPROX|KETORO|COXIB|FENAC",
             df3$NQ12_CPM_ACT)] <- "NSAIDS"
df3$MED[is.na(df3$MED)] <- "OTHER"
df2 <- df2[,c(1,3)]
df2 <- unique(df2)
df2$TIME <- "M06"
df3 <- df3[,c(1,3)]
df3 <- unique(df3)
df3$TIME <- "M12"
df4 <- dplyr::bind_rows(list(df1,df2,df3))
ggplotly(
  ggplot(df4, aes(fill=factor(MED), x=factor(TIME))) + 
    geom_bar(position="dodge") +
    labs(x = "Time", y = "Counts", title = "Pain medications intake") +
    theme_classic() + 
    scale_fill_viridis_d() +
    theme(axis.line = element_line(colour = 'black', size = 1),
          axis.ticks = element_line(colour = "black", size = 1),
          axis.text = element_text(color = "black", size = 15),
          axis.title = element_text(color = "black", size = 15),
          legend.title = element_blank(),
          legend.text = element_text(color = "black", size = 10))
)
```

## Statistical modeling

### Data preparation

```{r include=T, warning=F,message=F}
df1 <- reshape2::dcast(df1, ID ~ MED, length) # note: only 815 unique IDs
df1[-1] <- lapply(df1[-1], factor)
df <- merge(df,df1,by = "ID", all.x = T)
dfl <- merge(dfl,df1,by = "ID", all.x = T)
```

#### Following generalized linear modeling approaches were considered:

### 1. Fixed effect models:

#### A. Welch Two Sample t-test

```{r include=T, warning=F,message=F}
dt <- df %>% dplyr::filter(!is.na(PAIN_CHANGE)) %>% 
  dplyr::filter(DIAGNOSIS == "Lower Back Pain") %>% 
  dplyr::select(PAIN_CHANGE, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER) %>% 
  pivot_longer(!PAIN_CHANGE, names_to = "Drug", values_to = "Group")
dt$Group <- as.factor(ifelse(
  dt$Group == 1, "treatment", "control"
))

ttestbyDrug <- function(myDrug) {
  bt <- filter(dt, Group=="treatment", Drug==myDrug)
  bc <- filter(dt, Group=="control", Drug==myDrug)
  
  b <- t.test(bt$PAIN_CHANGE, bc$PAIN_CHANGE, conf.level=0.90)
  
  dataDrugPAIN_CHANGE <- data.frame(Drug = myDrug,
                          treatment = round(b$estimate[[1]], digits = 3),
                          control = round(b$estimate[[2]], digits = 3),
                          CI = paste('(',round(b$conf.int[[1]], 
                                               digits = 2),', ',
                                     round(b$conf.int[[2]], 
                                           digits = 2), ')',
                                     sep=""),
                          pvalue = round(b$p.value, digits = 3),
                          ntreatment = nrow(bt),  # changes only in
                          ncontrol = nrow(bc))    # these 2 nrow() args
}
T_Test <- dt$Drug %>% 
  unique %>% 
  lapply(., ttestbyDrug) %>% rbindlist
T_Test$total_N <- T_Test$ntreatment + T_Test$ncontrol
T_Test %>%
  kbl(caption = "Effect of drug intake on change in LBP scores") %>%
  kable_classic("hover", html_font = "Cambria", full_width = F) %>% scroll_box(width = "100%")
```

```{r include=T, warning=F,message=F}
dt <- df %>% dplyr::filter(!is.na(PAIN_CHANGE)) %>% 
  dplyr::filter(DIAGNOSIS == "Neuropathic Pain") %>% 
  dplyr::select(PAIN_CHANGE, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER) %>% 
  pivot_longer(!PAIN_CHANGE, names_to = "Drug", values_to = "Group")
dt$Group <- as.factor(ifelse(
  dt$Group == 1, "treatment", "control"
))

ttestbyDrug <- function(myDrug) {
  bt <- filter(dt, Group=="treatment", Drug==myDrug)
  bc <- filter(dt, Group=="control", Drug==myDrug)
  
  b <- t.test(bt$PAIN_CHANGE, bc$PAIN_CHANGE, conf.level=0.90)
  
  dataDrugPAIN_CHANGE <- data.frame(Drug = myDrug,
                          treatment = round(b$estimate[[1]], digits = 3),
                          control = round(b$estimate[[2]], digits = 3),
                          CI = paste('(',round(b$conf.int[[1]], 
                                               digits = 2),', ',
                                     round(b$conf.int[[2]], 
                                           digits = 2), ')',
                                     sep=""),
                          pvalue = round(b$p.value, digits = 3),
                          ntreatment = nrow(bt),  # changes only in
                          ncontrol = nrow(bc))    # these 2 nrow() args
}
T_Test <- dt$Drug %>% 
  unique %>% 
  lapply(., ttestbyDrug) %>% rbindlist
T_Test$total_N <- T_Test$ntreatment + T_Test$ncontrol
T_Test %>%
  kbl(caption = "Effect of drug intake on change in neuropathic pain scores") %>%
  kable_classic("hover", html_font = "Cambria", full_width = F) %>% scroll_box(width = "100%")

```

#### B1. Linear regression (change in LBP \~ Drug + age + sex + BMI + clinic)

```{r include=T, warning=F,message=F}
# models
dt <- df %>% dplyr::filter(!is.na(PAIN_CHANGE)) %>% 
  dplyr::filter(DIAGNOSIS == "Lower Back Pain") %>% 
  dplyr::select(PAIN_CHANGE, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER, AGE, SEX, BMI, CLINIC)

m1ac <- glm(PAIN_CHANGE ~ AGE + SEX + BMI + CLINIC + ACETAMINOPHEN,
            family = "gaussian",
            data = dt)
m1gb <- glm(PAIN_CHANGE ~ GABA_ANALOGS + AGE + SEX + BMI + CLINIC,
            family = "gaussian", 
            data = dt)
m1op <- glm(PAIN_CHANGE ~ OPIOIDS + AGE + SEX + BMI + CLINIC,
            family = "gaussian",
            data = dt)
m1ns <- glm(PAIN_CHANGE ~ NSAIDS + AGE + SEX + BMI + CLINIC,
            family = "gaussian", 
            data = dt)
export_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE,
             error_format = "[{conf.low}, {conf.high}]")

```
```{r include=T, warning=F,message=F}
plot_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE, plot.distributions = TRUE)
```

#### B2. Linear regression (change in Neuropathic Pain \~ Drug + age + sex + BMI + clinic)

```{r include=T, warning=F,message=F}
# models
dt <- df %>% dplyr::filter(!is.na(PAIN_CHANGE)) %>% 
  dplyr::filter(DIAGNOSIS == "Neuropathic Pain") %>% 
  dplyr::select(PAIN_CHANGE, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER, AGE, SEX, BMI, CLINIC)

m1ac <- glm(PAIN_CHANGE ~ AGE + SEX + BMI + CLINIC + ACETAMINOPHEN,
            family = "gaussian",
            data = dt)
m1gb <- glm(PAIN_CHANGE ~ GABA_ANALOGS + AGE + SEX + BMI + CLINIC,
            family = "gaussian", 
            data = dt)
m1op <- glm(PAIN_CHANGE ~ OPIOIDS + AGE + SEX + BMI + CLINIC,
            family = "gaussian",
            data = dt)
m1ns <- glm(PAIN_CHANGE ~ NSAIDS + AGE + SEX + BMI + CLINIC,
            family = "gaussian", 
            data = dt)
export_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE,
             error_format = "[{conf.low}, {conf.high}]")

```
```{r include=T, warning=F,message=F}
plot_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE, plot.distributions = TRUE)
```

#### C1. Linear regression (follow-up LBP \~ Drug + baseline LBP + age + sex + BMI + clinic)

```{r include=T, warning=F,message=F}
# models
dt <- df %>% dplyr::filter(!is.na(PAIN_CHANGE)) %>% 
  dplyr::filter(DIAGNOSIS == "Lower Back Pain") %>% 
  dplyr::select(PAIN_BASELINE, PAIN_FOLLOW_UP, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER, AGE, SEX, BMI, CLINIC)

m1ac <- glm(PAIN_FOLLOW_UP ~ AGE + SEX + BMI + CLINIC + PAIN_BASELINE + ACETAMINOPHEN,
            family = "gaussian",
            data = dt)
m1gb <- glm(PAIN_FOLLOW_UP ~ GABA_ANALOGS + AGE + SEX + BMI + CLINIC + PAIN_BASELINE,
            family = "gaussian", 
            data = dt)
m1op <- glm(PAIN_FOLLOW_UP ~ OPIOIDS + AGE + SEX + BMI + CLINIC + PAIN_BASELINE,
            family = "gaussian",
            data = dt)
m1ns <- glm(PAIN_FOLLOW_UP ~ NSAIDS + AGE + SEX + BMI + CLINIC + PAIN_BASELINE,
            family = "gaussian", 
            data = dt)
export_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE,
             error_format = "[{conf.low}, {conf.high}]")

```
```{r include=T, warning=F,message=F}
plot_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE, plot.distributions = TRUE)
```

#### C2. Linear regression (follow-up NP \~ Drug + baseline NP + age + sex + BMI + clinic)

```{r include=T, warning=F,message=F}
# models
dt <- df %>% dplyr::filter(!is.na(PAIN_FOLLOW_UP)) %>% 
  dplyr::filter(DIAGNOSIS == "Neuropathic Pain") %>% 
  dplyr::select(PAIN_BASELINE, PAIN_FOLLOW_UP, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER, AGE, SEX, BMI, CLINIC)

m1ac <- glm(PAIN_FOLLOW_UP ~ AGE + SEX + BMI + CLINIC + PAIN_BASELINE + ACETAMINOPHEN,
            family = "gaussian",
            data = dt)
m1gb <- glm(PAIN_FOLLOW_UP ~ GABA_ANALOGS + AGE + SEX + BMI + CLINIC + PAIN_BASELINE,
            family = "gaussian", 
            data = dt)
m1op <- glm(PAIN_FOLLOW_UP ~ OPIOIDS + AGE + SEX + BMI + CLINIC + PAIN_BASELINE,
            family = "gaussian",
            data = dt)
m1ns <- glm(PAIN_FOLLOW_UP ~ NSAIDS + AGE + SEX + BMI + CLINIC + PAIN_BASELINE,
            family = "gaussian", 
            data = dt)
export_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE,
             error_format = "[{conf.low}, {conf.high}]")
```
```{r include=T, warning=F,message=F}
plot_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE, plot.distributions = TRUE)
```

### 2. Mixed effect models:
#### A1. Linear regression (change in LBP \~ Drug + age + sex + BMI + (1 | clinic))

```{r include=T, warning=F,message=F}
# models
dt <- df %>% dplyr::filter(!is.na(PAIN_CHANGE)) %>% 
  dplyr::filter(DIAGNOSIS == "Lower Back Pain") %>% 
  dplyr::select(PAIN_CHANGE, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER, AGE, SEX, BMI, CLINIC)

m1ac <- lmer(PAIN_CHANGE ~ AGE + SEX + BMI + (1 | CLINIC) + ACETAMINOPHEN,
            data = dt)
m1gb <- lmer(PAIN_CHANGE ~ GABA_ANALOGS + AGE + SEX + BMI + (1 | CLINIC),
            data = dt)
m1op <- lmer(PAIN_CHANGE ~ OPIOIDS + AGE + SEX + BMI + (1 | CLINIC),
            data = dt)
m1ns <- lmer(PAIN_CHANGE ~ NSAIDS + AGE + SEX + BMI + (1 | CLINIC),
            data = dt)
export_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE,
             error_format = "[{conf.low}, {conf.high}]")

```
```{r include=T, warning=F,message=F}
plot_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE, plot.distributions = TRUE)
```

#### A2. Linear regression (change in NP \~ Drug + age + sex + BMI + (1 | clinic))

```{r include=T, warning=F,message=F}
# models
dt <- df %>% dplyr::filter(!is.na(PAIN_CHANGE)) %>% 
  dplyr::filter(DIAGNOSIS == "Neuropathic Pain") %>% 
  dplyr::select(PAIN_CHANGE, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER, AGE, SEX, BMI, CLINIC)

m1ac <- lmer(PAIN_CHANGE ~ AGE + SEX + BMI + (1 | CLINIC) + ACETAMINOPHEN,
            data = dt)
m1gb <- lmer(PAIN_CHANGE ~ GABA_ANALOGS + AGE + SEX + BMI + (1 | CLINIC),
            data = dt)
m1op <- lmer(PAIN_CHANGE ~ OPIOIDS + AGE + SEX + BMI + (1 | CLINIC),
            data = dt)
m1ns <- lmer(PAIN_CHANGE ~ NSAIDS + AGE + SEX + BMI + (1 | CLINIC),
            data = dt)
export_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE,
             error_format = "[{conf.low}, {conf.high}]")

```
```{r include=T, warning=F,message=F}
plot_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE, plot.distributions = TRUE)
```

#### B1. Linear regression (follow-up LBP \~ Drug + baseline LBP + age + sex + BMI + (1 | clinic)

```{r include=T, warning=F,message=F}
# models
dt <- df %>% dplyr::filter(!is.na(PAIN_CHANGE)) %>% 
  dplyr::filter(DIAGNOSIS == "Lower Back Pain") %>% 
  dplyr::select(PAIN_BASELINE, PAIN_FOLLOW_UP, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER, AGE, SEX, BMI, CLINIC)

m1ac <- lmer(PAIN_FOLLOW_UP ~ AGE + SEX + BMI + (1 | CLINIC) + PAIN_BASELINE + ACETAMINOPHEN,
            data = dt)
m1gb <- lmer(PAIN_FOLLOW_UP ~ GABA_ANALOGS + AGE + SEX + BMI + (1 | CLINIC) + PAIN_BASELINE,
            data = dt)
m1op <- lmer(PAIN_FOLLOW_UP ~ OPIOIDS + AGE + SEX + BMI + (1 | CLINIC) + PAIN_BASELINE,
            data = dt)
m1ns <- lmer(PAIN_FOLLOW_UP ~ NSAIDS + AGE + SEX + BMI + (1 | CLINIC) + PAIN_BASELINE,
            data = dt)
export_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE,
             error_format = "[{conf.low}, {conf.high}]")

```
```{r include=T, warning=F,message=F}
plot_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE, plot.distributions = TRUE)
```

#### B2. Linear regression (follow-up NP \~ Drug + baseline NP + age + sex + BMI + clinic)

```{r include=T, warning=F,message=F}
# models
dt <- df %>% dplyr::filter(!is.na(PAIN_FOLLOW_UP)) %>% 
  dplyr::filter(DIAGNOSIS == "Neuropathic Pain") %>% 
  dplyr::select(PAIN_BASELINE, PAIN_FOLLOW_UP, ACETAMINOPHEN, GABA_ANALOGS, 
         NSAIDS, OPIOIDS, OTHER, AGE, SEX, BMI, CLINIC)

m1ac <- lmer(PAIN_FOLLOW_UP ~ AGE + SEX + BMI + (1 | CLINIC) + PAIN_BASELINE + ACETAMINOPHEN,
            data = dt)
m1gb <- lmer(PAIN_FOLLOW_UP ~ GABA_ANALOGS + AGE + SEX + BMI + (1 | CLINIC) + PAIN_BASELINE,
            data = dt)
m1op <- lmer(PAIN_FOLLOW_UP ~ OPIOIDS + AGE + SEX + BMI + (1 | CLINIC) + PAIN_BASELINE,
            data = dt)
m1ns <- lmer(PAIN_FOLLOW_UP ~ NSAIDS + AGE + SEX + BMI + (1 | CLINIC) + PAIN_BASELINE,
            data = dt)
export_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE,
             error_format = "[{conf.low}, {conf.high}]")

```
```{r include=T, warning=F,message=F}
plot_summs(m1ac, m1gb, m1op, m1ns, scale = TRUE, plot.distributions = TRUE)
```

```{r include=T, warning=F,message=F}
sessionInfo()
```
